\documentclass{article}
\usepackage{projstyle}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{enumitem}

\title{A Brief Introduction to Legendrian Knots}
\author{Shreyas Casturi\\Ana Fishburn}
\date{5 November 2018}

\begin{document}

\maketitle

\begin{abstract}
We start by defining Legendrian knots and isotopies of Legendrian knots.
Then we study the classical invariants of Legendrian knots:
the topological knot type, the Thurston-Bennequin number, and the rotation number.
We then explain how, while sufficient for certain classes of knots in tight
contact structures, there are nonisotopic Legendrian knots with equal
In particular, we introduce the Chekanov-Eliashberg DGA, and see that its
homology, the knot contact homology, is an invariant. We see how this
can be computed to distinguish versions of the $5_2$ knot with equal classical
invariants.
\end{abstract}

\section{Introduction}
A {\it contact structure} on $\R^3$ is a method of placing a plane at every point,
such that these planes satisfy certain technical conditions.
There are various distinct contact structures we could use, some of them giving
very different properties.
However, for this paper, we will exclusively consider the standard contact structure:
At every point in $\R^3$, we consider the plane spanned by
\[\left\{\frac{\partial}{\partial y},\frac{\partial}{\partial x} + y\frac{\partial}{\partial z}\right\}.\]
Visually, we can see that these planes are always tangent to the $y$-axis, but also
twist around once when moving from $y = -\infty$ to $y = \infty$.

Now that we have this contact structure, we can define a {\it Legendrian knot}
as a knot that is at every point tangent to the plane at that point.
In particular, if we look at the tangent vector $v$ to $K$ at a point $p = (x,y,z)$,
then
\[ v = A\frac{\partial}{\partial y} + B\left(\frac{\partial}{\partial x} +y\frac{\partial}{\partial z}\right)\]
for some real numbers $A$ and $B$.
We can equivalently formulate this condition using a parametrization of $K$ as
the image of a smooth embedding $\phi : [0,1] \to \R^3$, where $\phi(t) = (x(t),y(t),z(t))$ satisfies
\[ z'(t)-y(t)x'(t) = 0.\]

We can now say that two Legendrian knots are equivalent if they can be related by a continuous
family of Legendrian knots. This is very similar to the definition of equivalence
for smooth knots, only here, we restrict the allowable motions.
Therefore, Legendrian equivalence is a finer relation than smooth knot equivalence,
and, in fact, we will show that there are many Legendrian inequivalent knots
with the same smooth knot type.

\section{Projections}
Before we can discuss invariants of Legendrian knots, we must first understand
the ways to visually represent them.
Because Legendrian knots rely on our choice of contact structure, and therefore
our choice of coordinates, dealing with projections of Legendrian knots will
be more complicated than with smooth knots.

The first method of projecting Legendrian knots is the {\it front projection}.
This is the projection onto the $xz$-plane. From the differential equation
$z'(t) = y(t)x'(t)$, we see that we can recover the $y$ coordinate from the front
projection by
\[y(t) = \lim_{t_0\to t}\frac{z'(t)}{x'(t)}.\]
We find the following two properties of front projections:
\begin{enumerate}[label=\roman*)]
\item There may be no vertical tangencies: if $x'(t)$ vanishes, so does $z'(t)$. Instead we 
allow {\it cusps}, points where the diagram forms a sharp horizontal point.
\item At each crossing, the under strand has greater slope than the over strand.
\end{enumerate}
It turns out that these conditions completely characterize front projections:
if $(x(t),z(t))$ satisfies these conditions, they are the coordinates of a Legendrian knot.
Furthermore, for any Legendrian knot, we can arrange for the set of cusp points to be finite.

We can take a projection of a smooth knot and convert it into the front
projection of a Legendrian knot by rotating each crossing until the under
strand has greater slope, and then
replacing vertical tangencies with cusps. We have therefore proved
\begin{theorem}
Every smooth knot may be realized as a Legendrian knot.
\end{theorem}

We now consider the harder to work with, but just as essential, {\it Lagrangian projection}.
This is the projection onto the $xy$-plane. This time, we must recover the $z$ coordinate
by integrating, so up to a constant $z_0$, we have
\[ z(t) = z_0 + \int_0^t y(s)x'(s)\,ds.\]
Now $(x(t),y(t))$ will provide a valid $z(t)$ if and only if
\begin{enumerate}[label=\roman*)]
\item $\int_0^1 y(s)x'(s)\,ds = 0$.
\item $\int_{t_1}^{t_2} y(s)x'(s)\,ds \neq 0$ whenever $(x(t_1),y(t_1))=(x(t_2),y(t_2))$.
\end{enumerate}

\section{Classical Invariants}
We now discuss the classical invariants related to Legendrian knots.  Given that a Legendrian
isotopy between two Legendrian knots is, at its core, an isotopy of the underlying knots, then the first
major invariant of the Legendrian knot is the \textit{topological knot type}, here donated as
$k(L).$ This is a rather intuitive notion.

The second major invariant is known as the \textit{Thurston-Bennequin invariant}, which essentially
measures how much coiling a given Legendrian knot has. Legendrian knots have what is called the
\textit{right cusp number}, essentially a measure of how many local right-cusps there are in its knot diagram.
These knots also have a quality known as the \textit{writhe } number, which is a measure of
counting the knot diagram's crossings, but only counting those crossings that have signs. To calculate
the maximal Thurston-Bennequin number, one can simply subtract the \textit{writhe} - \textit{right cusp number}.

This number calculated is the invariant. 
According to the Knot Atlas, the Thurston-Bennequin invariant is not just this number, but rather
the maximum number of a set of two numbers - the two maximal Thurston-Bennequin numbers
calculated for both the original knot diagram and its mirror. 

Rigorously speaking, following in Etnyre's footsteps, we may define the Thurston-Bennequin invariant
by using the idea of a bundle and its trivialization. Here, we denote a bundle as a \textit{vector bundle},
a collection of vector spaces that are parameterized by another space. Let us denote a normal, or perpendicular
bundle of a Legendrian knot $L$ by $v$. A \textit{trivialization} of $v$ is given as identifying $v$ with
$L \cdot \mathbb{R}^{2}$ (I use \textit{cdot} because I could not find a good symbol for the product).
Legendrian knots have what are called \textit{line bundles}, which use a Legendrian knot's canonical framing
to give a framing of $v$ ove $L$.

Given some normal bundle, we define a number $tw$ as the twisting of $l$ with respect to a
normal bundle's \textit{preassigned} framing. If $L$ is null-homologous, then $L$ has
a framing given by a Seifert surface, and the twisting of $L$ with respect to this surface
is known as the Thurston-Bennequin invariant of $L$, and is denoted as $tb(L).$

We now come to the last classical invariant: \textit{rotation number}. We define 
this invariant only for null-homologous knots.
We assume that $L$ has an embedded, orientable surface. When the contact planes
for this knot are restricted only to those planes that intersect this surface create
a trivialization by giving a two-dimensional bundle - as Etnyre states, over a surface with boundary,
in this case the embedded, orientable surface, any orientable two plane bundle is trivial. Given this
trivialization, we acquire another trivialization which is the product of $L$ and $\mathbb{R}^{2.}$
If we denote a non-zero vector field $v$ as one tangent to $L$, pointing in the direction of the orientation given on $L$,
we can imagine $v$ as a path of vectors in $\mathbb{R}^{2}$, then we realize there is a \textit{winding number} for these vectors,
and this \textit{winding number} is the rotation number of $L.$ Given that we used the orientation of L in determinng \textit{rotation number},
we can say the \textit{rotation number} is dependent upon the orientation of $L$ and will accordingly change signs if there is a change in
orientation.

We have, in a non-rigorous way, defined our three classical invariants. We now want to find the calculation of the \textit{rotation number}
as an end to this section.

We have to simply find how many times a non-zero tangent vector field $v$ that is in $\mathbb{R}^{2}$ goes, or winds, around
the origin of $\mathbb{R}^{2}$. This involves making a count of how many times our trivialization and $v$ point in the same direction/
are oriented the same way; this of course creates an intersection between $v$ and our trivialization. We determine the sign
at each intersection by figuring out if $v$ passes the trivialization clockwise or counter-clockwise ($1, -1$, respectively).
We then notice that the down and up cusps of our diagram also show whether an intersection will be positive or negative,
and as this counts the number of times $v$ intersects our trivialization, we just need to divide by two.
So the formula is:
\[r(L) = \frac{1}{2}(D - U) \]
We conclude the rough draft here.
\section{Chekanov-Eliashberg DGA}

\textit{This will be added in later, and is not part of the rough draft.}


\begin{thebibliography}{9}
\bibitem{etnyre}
    J. Etnyre,
    \textit{Legendrian and Transversal Knots},
    from: Handbook of Knot Theory,
    Elsevier B. V.,
    Amsterdam (2005).

\bibitem{sabloffRulings}
    J. Sabloff,
    \textit{Augmentations and Rulings of Legendrian Knots},
    Int. Math. Res. Not. (2005) 1157-1180.

\bibitem{sabloffAMS}
    J. Sabloff,
    \textit{What Is $\ldots$ a Legendrian Knot?},
    AMS Notices, 56 (2009), no. 10, 1282-1284.
\end{thebibliography}

\end{document}
